Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-12-24 paper.tex
Add description of wind model

The matter potential along this test ray is from an analytic wind
model qualitatively consistent with the densities in the
simulated volume (i.e.\ inside $r\sim70$~km) and asymptoting to the $r^{-3}$
density field of a spherical steady-state wind.
\footnote{TODO: confirm whether this is accurate}
The rest density from this model is plotted in Fig.~\ref{fig:test_traj_density}.
\footnote{TODO: cite Surman \& McLaughlin ApJ 618, 2005}

>>>>

The matter potential along this test ray is from an analytic wind
model qualitatively consistent with the densities in the
simulated volume (i.e.\ inside $r\sim70$~km) and asymptoting to the $r^{-2}$
density field of a spherical steady-state wind with a constant asymptotic
velocity.
The velocity and density fields of a spherical steady-state wind
obey the continuity equation $\rho(r)v(r)r^2=\rho_1 v_1 r_1^2$,
with $\rho_1$ and $v_1$ the density and velocity measured at some fiducial
radius $r_1$.
For velocity field we choose a phenomenological wind model used in the
oscillation literature\footnote{TODO: cite Surman \& McLaughlin ApJ 618, 2005}
\begin{equation}
  v(r) = v_1 \left(1-\frac{R}{r_1}\right)^{-\beta}
  \left(1-\frac{R}{r}\right)^{\beta},
\end{equation}
with $R$ the wind launch radius and $\beta$ an acceleration parameter.
This yields the following density field
\begin{equation}
  \rho(r)=\rho_1 C\left[\frac{r_1}{R}\right]
  \left(1-\frac{R}{r}\right)^{-\beta}\left(\frac{R}{r}\right)^2,
\end{equation}
with $C[a]=a^{2-\beta}(a-1)^\beta$.
We use the parameters $R=10$~km, $R_1=50$~km, $\beta=2$,
and $\rho_1=10^7\,{\rm g}\,{\rm cm}^{-3}$.
Additionally we impose a density cap of
$\rho_{\rm max}=10^{14}\,{\rm g}\,{\rm cm}^{-3}$ inside the radius $r_0=5$~km,
and smoothly interpolate densities between $r_0$ and $r_1$ with a cubic polynomial,
enforcing $C^0$ and $C^1$ continuity at the transitions.
The rest density from this model is plotted in Fig.~\ref{fig:test_traj_density}.
To translate this density field to a matter potential, we assume a constant
electron fraction of $Y_e=0.5$.
